TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
Edit section 1 a little

\todo{JU review: Still feels more like an intro than an abstract. Could be
shorter and punchier.}
\begin{abstract}
Formalization of mathematics in interactive theorem provers (ITPs)
relies today on many proof automation methods.
Some of these methods are general-purpose and with enough time they can prove any
theorem. Many formalized proof scripts however also
take advantage of specialized rules and theory-based strategies.
In the HOL4 ITP system, practically all of them are implemented as \emph{tactics}.

Automated theorem provers (ATPs) rely on parameterizable general
strategies. Sometimes, a strategy can be specialized for only one theory as in
SMT solving. But it is difficult for an automated theorem prover to rely on
rules tailored for a particular case.
Indeed, this would require implementing many specific rules and more
importantly figuring out in which cases they can be applied.

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function 
that takes a goal (or proof obligation) and returns a list of goals together 
with a validation function. \todoi{do not mention validation?}

\subsection{Contributions}
This work is an extension of the work described in \cite{tgckju-lpar17}.
There we proposed the idea of ... and achieved ...
The additional contributions and their effect on our system are:

>>>>

\todo{JU review: Still feels more like an intro than an abstract. Could be
shorter and punchier.}
\begin{abstract}
Formalization of mathematics in interactive theorem provers (ITPs) relies today on many proof automation methods.
Some of these methods are general-purpose and with enough time they can prove any provable conjecture.
Many formalized proof scripts however also take advantage of specialized rules and theory-based strategies.
In the HOL4 ITP system, practically all of them are implemented as \emph{tactics}.

Automated theorem provers (ATPs) rely on parameterizable general
strategies. Sometimes, a strategy can be specialized for only one theory as in
SMT solving. But it is difficult for an ATP to rely on rules tailored for a particular case.
Indeed, this would require implementing many specific rules and more
importantly figuring out in which cases they can be applied.

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof construction.
\todo{do not mention validation? RK: it depends whether these details are helpful for understanding or not}

\subsection{Contributions}
This paper extends the work described in \cite{tgckju-lpar17}.
There we proposed the idea of ... and achieved ...
The additional contributions and their effect on our system are:
